Climate indicators

### 2023-02-28 DRAFT_climate_indicators.Rmd
move to server

myFiles <- list.files(path2, pattern=".nc$",full.names = T)[1:2]
start_month <-  "06"
end_month <- "08"
real_temp_summer <- NULL

@@

  tic("init")
  temp <- stars::read_ncdf(paste(myFiles[i]), var="tg", proxy=F,
                           ncsub = cbind(start = c(1, 1, julian_start), 
                              count = c(NA, NA, step)))
  year_temp <- year(st_get_dimension_values(temp, "time")[1])
  start <- ym(paste(year_temp, start_month, sep="-"))
  end <-  ym(paste(year_temp, end_month, sep="-"))
  #myInterval <- interval(start, end)
  myInterval <- interval(start, start+1)
  lookup <- setNames("mean", paste0("v_", year_temp))
  st_crs(temp) <- 25833
  toc()

  tic("middle")
  temp <- temp %>%
    filter(time %within% myInterval) %>%
    st_apply(1:2, mean) %>%
    rename(all_of(lookup)) 
  toc()

  tic("c")
  real_temp_summer <- c(temp, real_temp_summer)
  #rm(temp)
  toc()
}

>>>>

myFiles <- list.files(path2, pattern=".nc$",full.names = T)[1:2]
real_temp_summer <- NULL

@@

  tic("init")
  temp <- stars::read_ncdf(paste(myFiles[i]), var="tg", proxy=F,
                           ncsub = cbind(start = c(1, 1, julian_start), 
                              count = c(NA, NA, step)))
  year_temp <- year(st_get_dimension_values(temp, "time")[1])
  #start <- ym(paste(year_temp, start_month, sep="-"))
  #end <-  ym(paste(year_temp, end_month, sep="-"))
  #myInterval <- interval(start, end)
  #myInterval <- interval(start, start+1)
  lookup <- setNames("mean", paste0("v_", year_temp))
  st_crs(temp) <- 25833
  toc()

  tic("filter and st_apply")
  temp <- temp %>%
    #filter(time %within% myInterval) %>%
    st_apply(1:2, mean) %>%
    rename(all_of(lookup)) 
  toc()

  tic("c()")
  real_temp_summer <- c(temp, real_temp_summer)
  #rm(temp)
  toc()
}
